\textsc{\wobble: a data-driven method for precision radial velocities}

### 2019-01-02 paper/paper.tex
minor edits
Former-commit-id: 86b55d216bc3795ee8c319b02702d7a1adbba712

We take the data to be the $M \times N$ matrix Y, where each entry $y_{m,n}$ is the observed logarithmic flux $\ln f$ for pixel $m$ of $M$ at epoch $n$ of $N$. orange
We also have a corresponding $M \times N$ matrix of wavelength solutions. 
Again, the entries of this matrix are in logarithmic form ($\ln \lambda$). 
This choice makes the Doppler shift an additive term, considerably simplifying the math to follow.

@@

\begin{figure*}
\centering
\includegraphics[width=6in]{hd189_rm}
\caption{\RVs measured by \wobble for a single night of observations of the Hot 
         Jupiter host HD 189733. The \RM is clearly seen as the planet transits 
         the star. The top panel shows the data (black points), the maximum
         likelihood fit using \starry (black curve), and 500 posterior samples
         (orange lines). The bottom panel shows the residuals of the maximum
         likelihood model fit.}
\label{fig:hd189_rm}
\end{figure*}

@@

\software{%
    astropy \citep{Astropy13, Astropy18},
    numpy \citep{Van-Der-Walt:2011},
    matplotlib \citep{Hunter:2007},
    scipy \citep{Jones:2001},
    tensorflow \citep{Abadi15}, 
    exoplanet \citep{exoplanet}
}

>>>>

We take the data to be the $M \times N$ matrix Y, where each entry $y_{m,n}$ is the observed logarithmic flux $\ln f$ for pixel $m$ of $M$ at epoch $n$ of $N$. 
We also have a corresponding $M \times N$ matrix of wavelength solutions. 
Again, the entries of this matrix are in logarithmic form ($\ln \lambda$). 
This choice makes the Doppler shift an additive term, considerably simplifying the math to follow.

@@

\begin{figure*}
\centering
\includegraphics[width=6in]{hd189_rm}
\caption{\RVs measured by \wobble for a single night of observations of the Hot 
         Jupiter host HD 189733. The \RM is clearly seen as the planet transits 
         the star. The top panel shows the data (black points), the maximum
         likelihood fit using \starry (black line), and 500 posterior samples
         (orange lines). The bottom panel shows the residuals of the maximum
         likelihood model fit.}
\label{fig:hd189_rm}
\end{figure*}

@@

\software{%
    astropy \citep{Astropy13, Astropy18},
    numpy \citep{Van-Der-Walt:2011},
    matplotlib \citep{Hunter:2007},
    scipy \citep{Jones:2001},
    tensorflow \citep{Abadi15}, 
    exoplanet \citep{exoplanet},
    starry \citep{Luger2018}
}
